Painting with Triangles

### 2014-06-05 paper.tex
foo
Changed graph labels and made changes based on reviewers suggestions.

Work has also been done in multi-resolution painting using raster graphics. The method of Berman~\etal~\shortcite{Berman:1994:MPC:192161.192181}
stores image information in a quadtree so that different parts of the image can have different levels of detail.
This means the image effectively has an infinite level of detail, yet since it is stored in raster form
there are still limitations. For example a stroke painted at coarse detail will still look blurry when
zoomed in. The strokes are limited to the resolution they are painted at. Similarly the method of Carr and Hart~\shortcite{Carr:2004:PD:1186562.1015809}
also allows the development of multi-resolution images using rasters, and as such suffers from the
same limitations. Another multi-resolution approach by Perlin and Velho~\shortcite{Perlin:1995:LPP:218380.218437} uses
procedural textures to avoid any fundamental limit on resolution. Although useful,
generating procedural textures can be difficult for artists.

@@

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke.
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$.

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision.

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to render. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

@@

@@

\ignorethis{
\section*{Acknowledgments}
Omitted for review.
}

>>>>

Work has also been done in multi-resolution painting using raster graphics. \modified{Early work with Pad++ by Bederson and Hollan~\shortcite{Bederson:1994:PZG:192426.192435} 
explored the possibility of having an infinite resolution canvas. However, rather than a general painting program 
this work is focused on creating an interface builder for developers.}
The method of Berman~\etal~\shortcite{Berman:1994:MPC:192161.192181}
stores image information in a quadtree so that different parts of the image can have different levels of detail.
This means the image effectively has an infinite level of detail, yet since it is stored in raster form
there are still limitations. For example a stroke painted at coarse detail will still look blurry when
zoomed in. The strokes are limited to the resolution they are painted at. Similarly the method of Carr and Hart~\shortcite{Carr:2004:PD:1186562.1015809}
also allows the development of multi-resolution images using rasters, and as such suffers from the
same limitations. \modified{One way to reduce blurriness in raster images of sharp features is proposed by Ramanarayanan~\etal~\shortcite{ramanarayanan2004feature}. 
By seprately storing where important boundaries are, their system can avoid excessive interpolation. However, such a method requires
creating such a data structure with those stored boundaries.} Another multi-resolution approach by Perlin and Velho~\shortcite{Perlin:1995:LPP:218380.218437} uses
procedural textures to avoid any fundamental limit on resolution. Although useful,
generating procedural textures can be difficult for artists.

@@

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke. \modified{This rasterization happens at the resolution of the current window. Therefore
whatever the artist sees on the screen is the basis for the vectorization.}
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$. \modified{We use
a threshold relative to zoom of 0.5 which was determined to work well empirically.}

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. \modified{Traditional vector
graphics software such as Adobe Illustrator caps zooming at a ratio of 64:1. Although this
is not an inherent limitation, there is currently not a way to use such vector graphics programs
to draw using a traditional painting metaphor with gradients while so zoomed in.}

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to render. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. \modified{For example, the first ten strokes in both cases take about 2 seconds
to render. While the last ten strokes take about 20 seconds in the non-zooming case and 7 seconds in the zooming case.}
It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

\modified{Note that all these numbers come from running the program on a 1.8 GHz Core i5 MacBook Air with 8GB of RAM and an Intel HD 4000 graphics card.}

@@

\modified{Beyond reducing the complexity of the geometry, the speed of the algorithm might be improved by
utilizing the GPU. For example, Nehab and Hoppe~\shortcite{Nehab:2008:RRG:1409060.1409088} demonstrate an
approach for using GPUs to speed up rending of more traditional vector graphics.}

@@

\modified{
\section*{Acknowledgments}
Let's add something here.
}
